---
title: "Active Learning - skin dataset trial"
author: "Meelad + Tyler"
date: "2/24/2019"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(glmnet)
library(reshape2)
library(feather)
```

```{r results='hide', warning=FALSE, message=FALSE}
# main <- read_csv("final_data_skin_NP.csv") %>% select(-X1, -image) %>% mutate(label = factor(label))
main <- read_feather("final_data_skin_NP.feather")
# data structure: 
## columns 1 to 1000 = featurized values
## column 1001 = data label

perf <- main %>% sample_frac(.15)
main <- main %>% setdiff(perf)
```

Here are several functions:
1. create_model_active and create_model_random create ridge regression models with the data, they store the model in a global variable.
2. generate_preds_active and generate_preds_random make predictions based on their corresponding generated model, they both log the results, and then only the generate_preds_active model calls a function to select the next 100 data points to add to the labeled data.
3.  store_performance and store_performance_rand_set both log the performance of their respective models in their respective data frames.
4.  select_data selects the next 100 data points to be labeled based on the "confidence" of the model's prediction of their class.

```{r warning=FALSE, message=FALSE}
# Items that need to be set up
perf_active_acc_table <- data.frame(round = NA, acc = NA)
perf_random_acc_table <- data.frame(round = NA, acc = NA)
active_accuracy_table <- data.frame(round = NA, acc = NA)
random_accuracy_table <- data.frame(round = NA, acc = NA)
confusion_matrices <- vector(mode = "list", length = 1000)
active_round <- 0
random_round <- 0

# Function for creating a model with data on active learning set
create_model_active <- function(df) {
  df <- df %>% mutate(label = factor(label))
  alpha <- 0.0
  lambda <- 0.5
  x_train <- model.matrix(~ ., select(df, -label))
  y_train <- df$label
  active_model <<- glmnet(x_train, y_train, alpha=alpha, 
                      lambda=lambda, 
                      family="multinomial")
}

# Function for creating a model with data on random set
create_model_random <- function(df) {
  df <- df %>% mutate(label = factor(label))
  alpha <- 0.0
  lambda <- 0.5
  x_train <- model.matrix(~ ., select(df, -label))
  y_train <- df$label
  random_model <<- glmnet(x_train, y_train, alpha=alpha, 
                      lambda=lambda, 
                      family="multinomial")
}

# Function for generating predictions on active learning set
generate_preds_active <- function(model, df) {
   x_test <- model.matrix(~ ., select(df, -label))
   category_prob <- predict(model, newx=x_test, type="response")
   preds <- predict(model, newx = x_test, type="class")
   max_probs <- apply(category_prob, 1, FUN = max)
   df <- cbind(df, max_probs)
   store_performance(df, preds)
   df <- df %>% arrange(max_probs)
   select_data(df)
}

# Function for generating predictions on random set
generate_preds_random <- function(model, df) {
   x_test <- model.matrix(~ ., select(df, -label))
   category_prob <- predict(model, newx=x_test, type="response")
   preds <- predict(model, newx = x_test, type="class")
   max_probs <- apply(category_prob, 1, FUN = max)
   df <- cbind(df, max_probs)
   store_performance_rand_set(df, preds)
   df <- df %>% arrange(max_probs)
}

# Function for logging accuracy of active learning set
store_performance <- function(df, preds) {
   active_round <- active_round + 1
   conf_mat <- table(df$label, preds)
   #confusion_matrices[[round]] <- conf_mat
   acc <- sum(conf_mat[1,1], conf_mat[2,2])/sum(conf_mat)
   temp <- data.frame(round = active_round, acc = acc)
   active_accuracy_table <<- rbind(active_accuracy_table, temp)
}

# Function for logging accuracy of random set
store_performance_rand_set <- function(df, preds) {
   random_round <- random_round + 1
   conf_mat <- table(df$label, preds)
   #confusion_matrices[[round]] <- conf_mat
   acc <- sum(conf_mat[1,1], conf_mat[2,2])/sum(conf_mat)
   temp <- data.frame(round = random_round, acc = acc)
   random_accuracy_table <<- rbind(random_accuracy_table, temp)
}

# Function for selecting data and changing datasets
select_data <- function(df) {
   df <- df %>% select(-max_probs)
   dat <<- rbind(dat, df[1:100,])
   remaining_dat <<- remaining_dat %>% setdiff(dat)
}

# Function for evaluation on performance set 
eval_perf <- function(model, df, i) {
   x_test <- model.matrix(~ ., select(df, -label))
   category_prob <- predict(model, newx=x_test, type="response")
   preds <- predict(model, newx = x_test, type="class")
   max_probs <- apply(category_prob, 1, FUN = max)
   df <- cbind(df, max_probs)
   conf_mat <- table(df$label, preds)
   acc <- sum(conf_mat[1,1], conf_mat[2,2])/sum(conf_mat)
   temp <- data.frame(round = 1, acc = acc)
   if (i == 1) {
     perf_active_acc_table <<- rbind(perf_active_acc_table, temp)
   } 
   if (i == 0) {
     perf_random_acc_table <<- rbind(perf_random_acc_table, temp)
   }
}
```


```{r results='hide'}
# Start off with 100
dat <- main %>% sample_n(100) # samples 100 from main
remaining_dat <- main %>% setdiff(dat) # takes the remaining samples left after sample_n

z <- 0
# And then loop through the rest of the data samples
for (x in 1:80) {
  # Active Data 
  create_model_active(dat)
  generate_preds_active(active_model, remaining_dat)
  # Random Data
  sample_size <- length(dat$X2)
  random_dat <- main %>% sample_n(sample_size)
  print(length(random_dat$X2))
  random_remaining_dat <- main %>% setdiff(random_dat)
  create_model_random(random_dat)
  generate_preds_random(random_model, random_remaining_dat)
  eval_perf(active_model, perf, 1)
  eval_perf(random_model, perf, 0)
  print("round complete")
  z <- z+1
  print(z)
}
```


```{r}
active_accuracy_table <- active_accuracy_table %>% select(-round)
perf_active_acc_table <- perf_active_acc_table %>% select(-round)
random_accuracy_table <- random_accuracy_table %>% select(-round)
perf_random_acc_table <- perf_random_acc_table %>% select(-round)

colnames(active_accuracy_table) <- c("train_active") 
colnames(random_accuracy_table) <- c("train_rand")
colnames(perf_active_acc_table) <- c("perf_active")
colnames(perf_random_acc_table) <- c("perf_rand")

ttl_acc <- cbind(active_accuracy_table, random_accuracy_table, perf_active_acc_table, perf_random_acc_table) %>% na.omit() 

round <- c(1:80)
ttl_acc <- cbind(round, ttl_acc)

ttl_acc_long <- melt(ttl_acc, id = "round")
ggplot(data = ttl_acc_long, aes(x=round, y=value, color = variable)) + geom_line()
```


